---
title: "Fluoroproj: Title to be decided later"
author: "Stephen D. Shivers, Sophie Fournier, Jakob Stankoski, Jeffrey W. Hollister, Betty J. Kreakie"
abstract: "This is our abstract.  Just seeing how it looks."
format: docx
bibliography: manuscript.bib
---

## Introduction

Possible Journals: Lake and Reservoir Management, PLOS One, PLOS Water, Ecosphere, F1000Research,

The goal of this paper is to compare accuracy and precision of a variety of fluorometers with respect to chlorophyll and phycocyanin across a variety of waterbodies as well as with lab grown cultures of green algae and cyanobacteria.

## Methods

When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
1 + 1
```

You can add options to executable code like this

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).

## Results

Here are our results. Fear us.

Figure ideas:

scatterplots: ext chl/phyco on y, chl/phyco from each insturment on x, colors/shapes for each waterbody/culture

boxplots (need to be same units): first boxplot is extracted, compare to all others.

## Discussion

Discuss amongst yourselves.

## References
